Constructor specialisation in GHC

### 2013-07-24 2013specconstr/Main.tex
ok

The core is quite a bit noisier.

@@

@@

@@

After inlining @foldl@, we get a recursive worker function.
\begin{code}
data Int = I# Int#

sum xs = go xs (I# 0#)
 where
  go []          (I# acc) = I# acc
  go ((I# x):xs) (I# acc) = go xs (I# (acc +# x))
\end{code}

@@

>>>>

The core is quite a bit noisier,
but it is easy to see that the idea is the same.

@@

\subsection{Simplifier}
The simplifier is the workhorse of GHC's optimisations.
It includes many different local transforms such as inlining, case-of-constructor, etc.

\subsection{Rewrite rules}

@@

\begin{code}
data Int = I# Int#

(+) :: Int -> Int -> Int
(+) (I# x) (I# y) = I# (x +# y)
\end{code}

With sufficient inlining and case-of-constructor simplification,
an arithmetic expression can be reduced to as few allocations as possible.

In the following sections, ints will be boxed and unboxed explicitly to make reductions in allocations more obvious.

@@

After inlining @foldl@, we get a recursive worker function.
\begin{code}
sum xs = go xs (I# 0#)
 where
  go []          (I# acc) = I# acc
  go ((I# x):xs) (I# acc) = go xs (I# (acc +# x))
\end{code}

@@

\subsection{Code blowup}
\subsection{Termination}
\subsection{ForceSpecConstr}
